---
title: "MESA Red Meat Metabolites Project"
author: "LekkiWood (LekkiWood@Gmail.com)"
date: today
format:
  pdf:
    pdf-engine: lualatex
    includes:
      in_header: 'gt_packages.sty'
    header-includes:
      - \usepackage{pdflscape}
      - \setkeys{Gin}{width=\linewidth,height=0.9\textheight,keepaspectratio}
    toc: true
    toc-depth: 4
execute:
  echo: false
  warning: false
  message: false
  # ensure chunks run from the project root (where _targets/ lives)
  dir: project
pdf-engine: latexmk
editor: visual
#bibliography: references.bib
---

```{r}
#| label: load-packages


## Load targets
if (!requireNamespace("targets", quietly = TRUE)) {
  stop("The {targets} package is not installed/available in this render session.")
}

## Load knitr
if (!requireNamespace("knitr", quietly = TRUE)) {
  stop("The {knitr} package is not installed/available in this render session.")
}

## Load quarto
if (!requireNamespace("quarto", quietly = TRUE)) {
  stop("The {quarto} package is not installed/available in this render session.")
}

## Load rcompanion
if (!requireNamespace("rcompanion", quietly = TRUE)) {
  stop("The {rcompanion} package is not installed/available in this render session.")
}

## Load Venn
if (!requireNamespace("VennDiagram", quietly = TRUE)) {
  stop("The {VennDiagram} package is not installed/available in this render session.")
}

## Load mixOmics
if (!requireNamespace("mixOmics", quietly = TRUE)) {
  stop("The {mixOmics} package is not installed/available in this render session.")
}

## Load Venn
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  stop("The {ggplot2} package is not installed/available in this render session.")
}
```

\newpage

# Important notes

-   You should always check you have the most recent files! I use dynamic dates, so this can be done by checking that your files match the dates on the latest GitHub versions:

    -   My profile can be found [here](https://github.com/LekkiWood)

    -   My repositories are listed [here](https://github.com/LekkiWood?tab=repositories)

    -   The most recent version of this PDF README file can be found [here](https://github.com/LekkiWood/MESA-Metabolomics-PCA/blob/main/MESA-Metabolomics-PCA.pdf)

    -   The most recent version of the source code for this README file can be found [here](https://github.com/LekkiWood/MESA-Metabolomics-PCA/blob/main/MESA-Metabolomics-PCA.qmd)

    -   The most recent source code for creating the output files can be found [here](https://github.com/LekkiWoodMESA-Metabolomics-PCA/blob/main/_targets.R)

# Summary

\newpage

# Data Preparation (Clary - you can probably ignore this)

## Metabolites

```{r}
#| label: load-file-info
#| cache: TRUE

######Metab File info

Metab_table_QC_info <- targets::tar_read(build_metabs_QC)
QC_info_mapping <- targets::tar_read(build_mapping_QC)
CV_table <- targets::tar_read(Metabolite_CV_and_missingness)
Duplicate_flag_file <- targets::tar_read(Duplicates_flag_file)
final_file_info <- targets::tar_read(Final_metabs_long_info)


path_amide <- targets::tar_read(path_amide)
path_C8 <- targets::tar_read(path_C8)
path_C18 <- targets::tar_read(path_C18)
path_HILIC <- targets::tar_read(path_HILIC)
path_amide_info <- targets::tar_read(path_amide_info)
path_C8_info <- targets::tar_read(path_C8_info)
path_C18_info <- targets::tar_read(path_C18_info)
path_HILIC_info <- targets::tar_read(path_HILIC_info)
path_bridge <- targets::tar_read(path_bridge)
```

### Input files

-   A table of metabolite abundances from the amide assay: `{r} print(unlist(strsplit(path_amide, split="/"))[7])`
-   A table of metabolite abundances from the C8-pos assay: `{r} print(unlist(strsplit(path_C8, split="/"))[7])`
-   A table of metabolite abundances from the C18-neg assay: `{r} print(unlist(strsplit(path_C18, split="/"))[7])`
-   A table of metabolite abundances from the HILIC assay: `{r} print(unlist(strsplit(path_HILIC, split="/"))[7])`
-   Sample information for the amide assay: `{r} print(unlist(strsplit(path_amide_info, split="/"))[7])`
-   Sample information for the C8-pos assay: `{r} print(unlist(strsplit(path_C8_info, split="/"))[7])`
-   Sample information for the C18-neg assay: `{r} print(unlist(strsplit(path_C18_info, split="/"))[7])`
-   Sample information for the HILIC assay: `{r} print(unlist(strsplit(path_HILIC_info, split="/"))[7])`
-   A file to bridge SHARe ids (sidno) with MESA IDs (idno) `{r} print(unlist(strsplit(path_bridge, split="/"))[7])`

### Build Raw Metabolite Tables

#### Amide

-   The amide sample info file contained information on N=`{r} Metab_table_QC_info$sample_info_dims$sample_info_dims_amide[1]` TOM IDs (each corresponding to one participant's abundances at one exam).
-   Duplicates were identified (see @tbl-amide-dupes) and removed.

```{r}
#| label: tbl-amide-dupes 
#| tbl-cap: "Duplicate IDs in raw amide assay data"
#| cache: TRUE

amide_dupes_table <- Metab_table_QC_info$duplicates_in_raw_tables$amide_dupes |>
  gt::gt() |>
  gt::tab_options(table.width = gt::pct(30)) |>
  gt::as_latex()

amide_dupes_table
```

-   Once the duplicates were removed, the final amide table contained data on N= `{r} Metab_table_QC_info$final_table_dims$final_table_dims_amide[2]-4` metabolites across `{r} Metab_table_QC_info$final_table_dims$final_table_dims_amide[1]` observations.

#### C8

-   The C8 sample info file contained information on N=`{r} Metab_table_QC_info$sample_info_dims$sample_info_dims_C8[1]` TOM IDs (each corresponding to one participant's abundances at one exam).
-   Duplicates were identified (see @tbl-C8-dupes) and removed.

```{r}
#| label: tbl-C8-dupes 
#| tbl-cap: "Duplicate IDs in raw C8 assay data"
#| cache: TRUE

C8_dupes_table <- Metab_table_QC_info$duplicates_in_raw_tables$C8_dupes |>
  gt::gt() |>
  gt::tab_options(table.width = gt::pct(30)) |>
  gt::as_latex()

C8_dupes_table
```

-   Once the duplicates were removed, the final amide table contained data on N= `{r} Metab_table_QC_info$final_table_dims$final_table_dims_C8[2]-4` metabolites across `{r} Metab_table_QC_info$final_table_dims$final_table_dims_C8[1]` observations.

#### C18

-   The C18 sample info file contained information on N=`{r} Metab_table_QC_info$sample_info_dims$sample_info_dims_C18[1]` TOM IDs (each corresponding to one participant's abundances at one exam).
-   Duplicates were identified (see @tbl-C18-dupes) and removed.

```{r}
#| label: tbl-C18-dupes 
#| tbl-cap: "Duplicate IDs in raw C8 assay data"
#| cache: TRUE

C18_dupes_table <- Metab_table_QC_info$duplicates_in_raw_tables$C18_dupes |>
  gt::gt() |>
  gt::tab_options(table.width = gt::pct(30)) |>
  gt::as_latex()

C18_dupes_table
```

-   Once the duplicates were removed, the final amide table contained data on N= `{r} Metab_table_QC_info$final_table_dims$final_table_dims_C18[2]-4` metabolites across `{r} Metab_table_QC_info$final_table_dims$final_table_dims_C18[1]` observations.

#### HILIC

-   The HILIC sample info file contained information on N=`{r} Metab_table_QC_info$sample_info_dims$sample_info_dims_HILIC[1]` TOM IDs (each corresponding to one participant's abundances at one exam).
-   Duplicates were identified (see @tbl-HILIC-dupes) and removed.

```{r}
#| label: tbl-HILIC-dupes 
#| tbl-cap: "Duplicate IDs in raw HILIC assay data"
#| cache: TRUE

HILIC_dupes_table <- Metab_table_QC_info$duplicates_in_raw_tables$HILIC_dupes |>
  gt::gt() |>
  gt::tab_options(table.width = gt::pct(30)) |>
  gt::as_latex()

HILIC_dupes_table
```

-   Once the duplicates were removed, the final amide table contained data on N= `{r} Metab_table_QC_info$final_table_dims$final_table_dims_HILIC[2]-4` metabolites across `{r} Metab_table_QC_info$final_table_dims$final_table_dims_HILIC[1]` observations.
-   The cleaned and transposed files from each assay were merged into a final, long form metabolite table with N=`{r} Metab_table_QC_info$final_df_info$final_metabs_merged_dim[1]` observations on `{r} Metab_table_QC_info$final_df_info$final_metabs_merged_dim[2]` variables (5 variables are not metabolites: sidno, subject_id, TOM_ID, exam, idno).

### Build Mapping file

-   The following variables were created:
    -   "Presence MESA X01" (coded 1)
    -   "Presence MESA PILOT" (coded 1)
    -   "Presence MESA MESA2" (coded 1).
-   The original metabolite name (where known) from the lab was preserved as the variable 'Original_Metabolite_Name'
-   A variable "Known_Compound" was created to indicate whether the compound had been assigned a name as of `{r} format(Sys.Date(), "%A, %B, %d, %Y")`^2^ (coding 1= yes, 0=no).
-   For unknown compounds, the lab ID (arbitrarily assigned by The Broad) assigned within the X01 study was used, and prefixed with the assay name.
-   The number of known/unknown compounds per assay is:
    -   Amide: N= `{r} print(Metab_table_QC_info$knowns$amide_knowns[1,2])` known compounds and no unknown compounds.
    -   C18: N= `{r} print(Metab_table_QC_info$knowns$C18_knowns[2,2])` known compounds and `{r} print(Metab_table_QC_info$knowns$C18_knowns[1,2])` unknown compounds.
    -   C8: N= `{r} print(Metab_table_QC_info$knowns$C8_knowns[2,2])` known compounds and `{r} print(Metab_table_QC_info$knowns$C8_knowns[1,2])` unknown compounds.
    -   HILIC: N= `{r} print(Metab_table_QC_info$knowns$HILIC_knowns[2,2])` known compounds and `{r} print(Metab_table_QC_info$knowns$HILIC_knowns[1,2])` unknown compounds.
-   The final mapping file has information on `{r} print(Metab_table_QC_info$knowns$all_knowns[2,2])` known compounds and `{r} print(Metab_table_QC_info$knowns$all_knowns[1,2])` unknown compounds

### Calculate QC data (missingness and CV)

#### Coefficients of Variation (CV)

-   For each of the four metabolite tables above, the QC samples for calculating the coefficient of variation (CV) were selected by selecting Sample_Type=="QC-pooled_ref" from the sample info files.
-   CVs were calculated across all exams (since batches were not stratified by exam) as the mean of all QC samples, divided by the standard deviation of all QC samples, multiplied by 100, and saved as the variable "cv_percent".
-   Across, all assays, the mean CV was `{r} mean(CV_table$cv_percent, na.rm=TRUE)`, with a range of `{r} min(CV_table$cv_percent, na.rm=TRUE)` - `{r} max(CV_table$cv_percent, na.rm=TRUE)`.
-   The CVs per assay, in @tbl-cvs-by-assay:

```{r}
#| label: tbl-cvs-by-assay
#| tbl-cap: "Coefficients of Variation by assay"
#| cache: TRUE


CV_table1 <- CV_table |>
  dplyr::group_by(Assay) |>
  dplyr::summarise(Mean_CV = mean(cv_percent, na.rm=TRUE)) |>
  gt::gt() |>
  gt::tab_options(table.width = gt::pct(30)) |>
  gt::as_latex()

CV_table1 

```

-   The CVs per assay, stratified into known and unknown metabolites are in @tbl-cvs-by-assay-by-known-status:

```{r}
#| label: tbl-cvs-by-assay-by-known-status
#| tbl-cap: "Coefficients of Variation by assay and exam"
#| cache: TRUE


CV_table2 <- CV_table |>
  dplyr::group_by(Assay, Known) |>
  dplyr::summarise(Mean_CV = mean(cv_percent, na.rm=TRUE)) |>
  dplyr::mutate(Known = dplyr::case_when(Known==1 ~ "Known Metabolites",
                                         Known==0 ~ "Unknown Compounds",
                                         TRUE ~ NA_character_)) 
CV_table2 <- CV_table2 |>
  gt::gt() |>
  gt::tab_options(table.width = gt::pct(50)) |>
  gt::fmt_number(decimals = 2) |>
  gt::as_latex() 

CV_table2

```

#### Missingness

-   The proportion of missingness for each assay, by exam is in @tbl-missingness-by-assay-by-exam (note, this is for people with assay data at each exam, missingness does not include, for example, people who have data at exam 1, but have no data at exam 5):

```{r}
#| label: tbl-missingness-by-assay-by-exam
#| tbl-cap: "Missingness by assay, and by exam"
#| cache: TRUE


CV_table3 <- CV_table |>
  dplyr::group_by(Assay) |>
  dplyr::summarise(Overall = mean(missing_all_exams, na.rm=TRUE),
                   E1 = mean(missing_exam_1, na.rm=TRUE),
                   E5 = mean(missing_exam_5, na.rm=TRUE),
                   E6 = mean(missing_exam_6, na.rm=TRUE)) |>
  gt::gt() |>
  gt::tab_options(table.width = gt::pct(90)) |>
  gt::as_latex()

CV_table3

```

### Removing duplicate metabolites

#### Annotation cleaning

-   Some light cleaning of the metabolite annotations was conducted (note: this is an ongoing process):
-   Glutamic acid had different HMDBs on the original HILIC and amide assays (see @tbl-glutamic-acid). Per advice: The HMDB from the HILIC was retained for both assays, and these were treated as the same compound.

|               |             |               |       |
|---------------|-------------|---------------|-------|
| Lab ID        | HMDB        | Metabolite    | Assay |
| QI18171       | HMDB0000148 | Glutamic acid | hilic |
| Glutamic.acid | HMDB0003339 | Glutamic acid | amide |

: HMDBs for Glutamic Acid in raw data {#tbl-glutamic-acid}

-   The metabolite Glutamic acid had the HMDB ID changed from HMDB0003339 `->` HMDB0000148.
-   For the amide assay, the compound with HMDB ID "HMDB0000122" had a different name to that used for the HILIC and C18 assays (see @tbl-HMDB0000122). Both names atr "correct", just different conventions, so these were treated as the same compounds when screening for duplicates.

+---------------------+---------------+---------------------+---------------+
| Lab ID              | HMDB          | Metabolite          | Assay         |
+---------------------+---------------+---------------------+---------------+
| Glucose.Fructose.   | HMDB0000122   | Glucose/Fructose/   | amide         |
|                     |               |                     |               |
| Galactose_waterloss |               | Galactose_waterloss |               |
+---------------------+---------------+---------------------+---------------+
| QI3656              | HMDB0000122   | Hexose              | c18           |
+---------------------+---------------+---------------------+---------------+
| QI14125             | HMDB0000122   | Hexose              | hilic         |
+---------------------+---------------+---------------------+---------------+

: Annotations for HMDB0000122 in raw data {#tbl-HMDB0000122}

#### Removing duplicated metabolites

-   The HMDB_ID variable was used to flag compounds measured on more than one assay
-   To flag metabolites included on more than one asssay, a variable was created "Retain", with the following coding:
    -   0, labelled "Unique or missing HMDB ID": an unknown compound, or a unique HMDB ID
    -   1, labelled "Duplicated HMDB ID with lowest CV": A duplicated HMDB ID with the lowest coefficient of variation (CV) across all compounds sharing that HMDB ID
    -   2, labelled "Internal standard": A compound used as an internal standard (generally excluded from standard analyses)
    -   3, labelled "Duplicated HMDB_ID and not lowest CV": A duplicated HMDB ID that does *not* have the lowest coefficient of variation (CV) across all compounds sharing that HMDB ID (generally excluded from analyses where you do not want the same compound included more than once)
-   See @tbl-dupe-metabs

```{r}
#| label: tbl-dupe-metabs
#| tbl-cap: "Information on metabolites included on more than one assay"
#| cache: TRUE



dupe_metabs_table <- as.data.frame(table(Duplicate_flag_file$Retain)) 

colnames(dupe_metabs_table) <- c("Metabolite Duplicate status", "Frequency (N)")

dupe_metabs_table2 <- dupe_metabs_table |>
  gt::gt() |>
  gt::tab_options(table.width = gt::pct(70)) |>
  gt::as_latex()

dupe_metabs_table2
```

-   All metabolites that had either a unique HMDB ID, or that had a duplicated HMDB ID but had the lowest CV from all those metabolites with the same HMDB ID were retained, all others were removed from the analysis.
-   The final metabolite file contained information on N=`{r} print(final_file_info)[2] - 5` metabolites across N=`{r} final_file_info[1]` observations.

### Some unresolved issues to note

-   The raw data from the C18 assay has a smaller N than some others

-   Most duplicated compounds are measured on different assays. One exception is LPC 16:0/0:0, which is measured twice on the C8 assay, with the same HMDB, but different assigned LAB IDs. For now, the compound with the Compound ID in the X01 of "TF04" is renamed as LPC 16:0/0:0_v2.

-   Some lipids have the same HMDB ID, but the different common metabolite names, and these names are not listed as synonyms in the [HMDB](https://www.hmdb.ca/) (e.g., Cer 40:1;O2 (C8 assay) is not listed as a synonym for 18:1 (HILIC), and Cer 42:2;O2_A (C8) is not listed for a synonym for Cer 18:1;O2/24:1 (HILIC). For now, these are treated as separate compounds (see @tbl-HMDB0004952 and @tbl-HMDB0004953).

|         |             |                  |       |
|---------|-------------|------------------|-------|
| Lab ID  | HMDB        | Metabolite       | Assay |
| QI04610 | HMDB0004952 | Cer 18:1;O2/22:0 | hilic |
| QI8023  | HMDB0004952 | Cer 40:1;O2      | c8    |

: Annotations for HMDB0004952 in raw data {#tbl-HMDB0004952}

|         |             |                  |       |
|---------|-------------|------------------|-------|
| Lab ID  | HMDB        | Metabolite       | Assay |
| QI04540 | HMDB0004953 | Cer 18:1;O2/24:1 | hilic |
| QI4265  | HMDB0004953 | Cer 42:2;O2_A    | c8    |

: Annotations for HMDB0004952 in raw data {#tbl-HMDB0004953}

\newpage

# Methods

## Procedure

## Analyses

### PCA

#### Data selection

As the modeling approach cannot accommodate missing data, a data-adaptive feature selection procedure to balance predictor inclusion with retention of participant-level completeness. Specifically, a greedy, forward-selection algorithm was applied in which candidate features (metabolites) were evaluated in blocks of 50 to improve computational efficiency. Within each iteration, the feature whose inclusion resulted in the smallest reduction in the number of eligible participants—defined as those with non-missing outcome data for true class membership—was selected from the evaluated block. Following selection, participant eligibility was recalculated based on complete-case availability for all included features. This process was repeated iteratively across successive blocks of candidate features, with features prioritized according to their minimal impact on sample retention. The procedure continued until inclusion of an additional feature would have reduced the analytic sample below a prespecified threshold of two-thirds of eligible participants.

#### Unsupervised analysis of underlying structure

To explore the underlying structure of the metabolite data without a priori hypotheses, an unsupervised principal component analysis (PCA) was conducted using the mixOmics package in R. PCA was applied to the set of selected features to reduce dimensionality and identify dominant axes of variation across participants. Prior to PCA analysis, continuous variables were standardized to have mean zero and unit variance to ensure comparability across features. The PCA algorithm decomposes the data into orthogonal components that successively capture the greatest variance in the dataset, with the first few components summarizing the primary patterns of variability. Component scores were used to visualize clustering and heterogeneity among participants, and loading vectors were examined to identify features contributing most strongly to each principal component. This unsupervised approach provided a data-driven summary of the multivariate structure, facilitating interpretation of complex relationships among features.

Because this is an exploratory analysis for data QC, and not for prediction, we did not use training and test datasets - the PCA was just run on the whole sample after selection via the greedy algorithm.

# Results

## Participant characteristics

Clary - tell me if you need this.

## PCA

```{r}
#| label: read-in-results-data

included_vars <- targets::tar_read(included_vars)
included_pps <- targets::tar_read(included_pps)
tune.pca <- targets::tar_read(tune.pca)
final.pca <- targets::tar_read(final.pca)
PCA_res <- targets::tar_read(PCA_res)
loadings_matrix <- targets::tar_read(loadings_matrix)

#Individual PCAs
pca_C8 <- targets::tar_read(pca_C8)
pca_C18 <- targets::tar_read(pca_C18)
pca_Amide <- targets::tar_read(pca_Amide)
pca_HILIC <- targets::tar_read(pca_HILIC)
```

-   The greedy algorithm selected N=`length(included_vars$Metabolite)` metabolites to include.

    -   A list of these can be found [here](https://github.com/LekkiWood/MESA-Metabolomics-PCA/blob/main/outputs/MESA_PCA_Metabolites.csv).

    -   A total of N=`{r} print(length(included_vars[included_vars$Assay=="Amide",]$Metabolite))`.     

    -   A total of N=`{r} print(length(included_vars[included_vars$Assay=="HILIC",]$Metabolite))` were from the HILIC assay.  

    -   A total of N=`{r} length(included_vars[included_vars$Assay=="C8",]$Metabolite)` were from the C8 assay

    -   A total of N=`{r} length(included_vars[included_vars$Assay=="C18",]$Metabolite)` were from the C18 assay

-   A total of N=`{r} print(included_pps)` MESA participants from exam 1 were included.

A scree plot suggested that a single component was chosen for the PCA @fig-tuning-comp.

```{r}
#| label: fig-tuning-comp
#| fig-cap: "Screeplot from the PCA performed on the MESA metabolite data"
#| cache: TRUE

plot(tune.pca)

```

A PCA was fit to the metabolite data with a single component.

-   Individual component scores with various MESA IDs / TOPMed IDs can be found [here](https://github.com/LekkiWood/MESA-Metabolomics-PCA/blob/main/outputs/MESA_PCA_Metabolites.csv). 
-   Variable loadings for each metabolite can be found [here](https://github.com/LekkiWood/MESA-Metabolomics-PCA/blob/main/outputs/MESA_loadings_matrix.csv).

There was clear clustering of the MESA participants within component 1 @fig-comp-1. This did not seem to be due to gender @fig-comp-1-gender (I also checked age, BMI, diabetes status, and lipids, as well as the metabolite technical covariates I could think of).

```{r}
#| label: fig-comp-1
#| fig-cap: "Distribution of scores for component 1"
#| cache: TRUE
 
mixOmics::plotIndiv(final.pca, 
          ind.names = TRUE, 
          legend = FALSE,  
          comp=c(1,1))
```

```{r}
#| label: fig-comp-1-gender
#| fig-cap: "Distribution of scores for component 1 by gender"
#| cache: TRUE

mixOmics::plotIndiv(final.pca, ind.names = TRUE, 
          group = as.numeric(PCA_res$gender1),
          legend = TRUE, 
          comp=c(1,1)
          )
          
```

### Assay specific results.

The loadings of the metabolites onto component 1, by assay, are in @fig-loadings-by-assay.

PCAs were run for each assay seperately, and the distribution of the extracted component plotted:

-   C8: @fig-PCA-C8

-   C18: @fig-PCA-C18

-   Amide: @fig-PCA-Amide

-   HILIC: @fig-PCA-HILIC

    ```{r}
    #| label: fig-loadings-by-assay
    #| fig-cap: "Distribution of scores for component 1 by gender"
    #| cache: TRUE

    ggplot2::ggplot(loadings_matrix, ggplot2::aes(x = PC1, fill = Assay)) +
      ggplot2::geom_histogram(alpha = 0.5, position = "identity")

    ```

```{r}
#| label: fig-PCA-C8
#| fig-cap: "Distribution of scores for component 1 for C8"
#| cache: TRUE
mixOmics::plotIndiv(pca_C8, 
          ind.names = TRUE,
          legend = FALSE, 
          comp=c(1,1)) 

```

```{r}
#| label: fig-PCA-C18
#| fig-cap: "Distribution of scores for component 1 for C18"
#| cache: TRUE
mixOmics::plotIndiv(pca_C18, 
          ind.names = TRUE,
          legend = FALSE, 
          comp=c(1,1)) 

```

```{r}
#| label: fig-PCA-Amide
#| fig-cap: "Distribution of scores for component 1 for Amide"
#| cache: TRUE
mixOmics::plotIndiv(pca_Amide, 
          ind.names = TRUE,
          legend = FALSE, 
          comp=c(1,1)) 

```

```{r}
#| label: fig-PCA-HILIC
#| fig-cap: "Distribution of scores for component 1 for HILIC"
#| cache: TRUE
mixOmics::plotIndiv(pca_HILIC, 
          ind.names = TRUE,
          legend = FALSE, 
          comp=c(1,1)) 

```
